Utilizing Parallel Workers: \\LLVM's Vectorization Plan

### 2024-11-11 paper/paper.tex
rough paper structure #3

\begin{enumerate}
  \item Modern CPUs (SIMD-Registers, SIMD ISAs)
  \item SIMD performance gains
  \item Auto-Vectorization to help programmers better utilize SIMD functionality out of the box
  \item LLVM as popular, platform-agnostic compiler framework
  \item auto-vectorization complexity $\rightarrow$ wish for well designed, 
  interoperable system (VPlan) $\rightarrow$ ongoing 8 year long effort started by Intel
\end{enumerate}

@@

\section{LLVM's Vectorization Plan}
\label{sec:vplan}
  Overview~\cite{llvmvec,llvmvplan,llvmextloopvec,llvmintrvplan,llvmvplanstate,llvmvplanrv,llvmouterloop,llvmvplanupdate}
\begin{enumerate}
  \item Phase 1: Legality
  \item Phase 2: Planning (Vectorization Plans)
  \begin{enumerate}
    \item Building initial VPlan based on Phase 1 Constraints (Generate one or more up-to-date Code Examples for VPlan similar to~\cite{llvmintrvplan,llvmvplanstate,llvmouterloop})
    $\rightarrow$ Explain different components (e.g.: \texttt{VPBasicBlock}, \texttt{VPRegionBlock}, etc.) and
    correlation between generated VPlan structure, original scalar code. Show some general optimizations.
    \item Modelling Cost (related work? already adopted?~\cite{POHL2020102106})
    \item Optimizing/Transforming VPlans
  \end{enumerate}
  \item Phase 3: Execution - Materialize best VPlan
\end{enumerate}

@@

\section{Summary and Future Work}
\label{sec:summary}
\begin{enumerate}
  \item VPlan Summary~\cite{llvmvplan,llvmvplanupdate}
  \item VPlan Future Roadmap~\cite{llvmvplan,llvmvplanupdate} (e.g.: combining outer-/inner-loop paths, full function vectorization, etc.)
  \item (Comparison/Outlook auto-vectorization and explicit vectorization~\cite{10.1155/2021/3264624, 9802745, DBLP:conf/vldb/BensonER23})
  (\cite{chinese180}~only in chinese?)
\end{enumerate}

>>>>

\begin{enumerate}
  \item Modern CPUs (SIMD-Registers, SIMD ISAs)
  \item SIMD performance gains
  \item Auto-Vectorization to help programmers better utilize SIMD functionality out of the box
  \item LLVM as popular, platform-agnostic compiler framework
  \item auto-vectorization complexity $\rightarrow$ wish for well designed, 
  interoperable system (VPlan) $\rightarrow$ ongoing 8 year long effort started by Intel
  \item rough paper outline
\end{enumerate}

@@

\section{LLVM's Vectorization Plan}
\label{sec:vplan}
  Overview~\cite{llvmvec,llvmvplan,llvmextloopvec,llvmintrvplan,llvmvplanstate,llvmvplanrv,llvmouterloop,llvmvplanupdate}
\begin{enumerate}
  \item Phase 1: Legality
  \item Phase 2: Planning (Vectorization Plans)
  \begin{enumerate}
    \item Building initial VPlan based on Phase 1 Constraints (Generate one or more up-to-date Code Examples for VPlan similar to~\cite{llvmintrvplan,llvmvplanstate,llvmouterloop})
    $\rightarrow$ Explain different components (e.g.: \texttt{VPBasicBlock}, \texttt{VPRegionBlock}, etc.) and
    correlation between generated VPlan structure, original scalar code. Show some general optimizations.
    \item Modelling Cost. Not yet part of VPlan. (related work? already adopted?~\cite{POHL2020102106})
    \item Optimizing/Transforming VPlans~\cite{llvmvplanupdate}
  \end{enumerate}
  \item Phase 3: Execution - Materialize best VPlan
\end{enumerate}

@@

\section{Summary and Future Work}
\label{sec:summary}
\begin{enumerate}
  \item VPlan Summary~\cite{llvmvplan,llvmvplanupdate}
  \item VPlan Future Roadmap~\cite{llvmvplan,llvmvplanupdate} (e.g.: combining outer-/inner-loop paths, full function vectorization, etc.)
  \item (Comparison/Outlook auto-vectorization and explicit vectorization~\cite{10.1155/2021/3264624, 9802745, DBLP:conf/vldb/BensonER23})
\end{enumerate}
